\documentclass[margin,centered]{res}
%global options Bryan took out:
%pifont,palatino,courier
\bibliographystyle{plainnat}



\usepackage{pifont}
\usepackage[latin1] { inputenc}

\topmargin -.5in
%\oddsidemargin -.5in
%\evensidemargin -.5in
%\textwidth=6.0in
 \textheight=9.0in
%\itemsep=0in
%\parsep=0in
\usepackage{fancyhdr}
%\topmargin=0in
%\textheight=8.5in
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\fancyhf{}
%\cfoot{\thepage}
%\lfoot{\textit{\footnotesize Research Statement}}
\rfoot{{\footnotesize Curriculum Vitae, Bryan D. Martin, \thepage}}


\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

%Bryan Added
\usepackage[letterspace=50]{microtype}
\usepackage{pifont}
\usepackage{color}
\usepackage{verbatim}

%\usepackage{libertineotf}
\usepackage{libertine}
\usepackage{microtype}
%make my CV machine unicode readable
\input{glyphtounicode}
\pdfgentounicode=1

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,      
    urlcolor=blue,
}
 
\urlstyle{same}

\begin{document}

\name{ Bryan D. Martin}
\vspace*{.1in}


\begin{resume}

\section{\sc Contact Information}

\vspace{.05in}
\begin{tabular}{@{}p{2.0in}p{2.9in}}
Department of Statistics& Email:  bmartin6@uw.edu \\
University of Washington  &Webpage: \href{https://bryandmartin.github.io/}{\texttt{bryandmartin.github.io}}
\\
Padelford B-317		                   	   \\
Seattle, WA, 98195             & \\






\end{tabular}

\section{\sc Education}
{\bf University of Washington}, Seattle, Washington
%\vspace*{-.1in}
\begin{list1}
\item[] 
Ph.D.~Statistics Student
\begin{list2}
\vspace*{.05in}
\item Research topic: Statistical model development for compositional data applied to the microbiome
\item Advisors: Daniela Witten and Amy Willis
\item Coursework: Statistical machine learning, convex optimization, statistical inference, stochastic modeling, cluster analysis, Bayesian statistics, spatial statistics, statistical computing, applied regression
\end{list2}
\end{list1}



{\bf Macalester College}, St. Paul, MN
%\vspace*{-.1in}
\begin{list1}
\item[] B.A.~Honors Applied Mathematics \& Statistics (summa cum laude), May 2015
\item[] B.A.~Economics (summa cum laude), May 2015
\begin{list2}
\vspace*{.05in}
\item Coursework: Mathematical statistics, econometrics, signal processing, real analysis, Bayesian statistics, probability, numerical analysis
\end{list2}
\end{list1}


\section{\sc Publications}

\textbf{Martin, B. D.}, Addona, V., Wolfson, J., Adomavicius, G., \& Fan, Y. (2017). Methods for real-time prediction of the mode of travel using smartphone-based GPS and accelerometer data. \textit{Sensors}, 17(9), 2058.

\section{\sc Submitted}

Tromas, N.,  Taranu, Z. E., \textbf{Martin, B. D.}, Willis, A., Greer, C. W., \& Shapiro, B. J. Niche separation increases with genetic distance among bloom-forming cyanobacteria.

Li, Z., Hsiao, Y., Godwin, J., \textbf{Martin, B. D.}, Wakefield, J., Clark, S. J. Changes in the spatial distribution of the under five mortality rate: small-area analysis of 136 DHS Surveys in 33 countries in Africa and Asia.


% In progress, probably don't need?
%\section{\sc In Progress}


\section{\sc Software} 

\cite{SUMMER}

\bibliography{bib}
\textbf{Martin, B. D.}, Li, Z. R. (2017). SUMMER: Spatio-Temporal Under-Five Mortality Methods for Estimation. \texttt{R} package.\\
\textbf{Availability:} \href{https://CRAN.R-project.org/package=SUMMER}{CRAN} and \href{https://github.com/bryandmartin/SUMMER}{Github}


\section{\sc Research\\ Experience}
{\bf University of Washington},  Seattle, Washington
\begin{list1}
\item[] 
Research Assistant, May 2017--Present
\begin{list2}
\vspace*{.05in}
\item Advisors: Daniela Witten and Amy Willis
\item Model development and statistical inference for compositional data applied to the microbiome
\item Manuscript in progress
%\item Smooth small-area estimates with Bayesian spatial methods
%\item Critical examination of the assumptions underlying simulation methods for trajectory models
\end{list2} 
\end{list1}


{\bf University of Washington},  Seattle, Washington
\begin{list1}
\item[] 
Research Assistant, January 2017--May 2017
\begin{list2}
\vspace*{.05in}
\item Advisor: Jon Wakefield
\item Used space-time models to combine data from multiple sources to provide reliable estimation of mortality rates using complex survey data
\item Manuscript in progress
%\item Smooth small-area estimates with Bayesian spatial methods
%\item Critical examination of the assumptions underlying simulation methods for trajectory models
\end{list2} 
\end{list1}

{\bf University of Washington},  Seattle, Washington
\begin{list1}
\item[] 
Research Assistant, January 2016--January 2017
\begin{list2}
\vspace*{.05in}
\item Advisor: Elena Erosheva
\item Developed a new unimodal mixed membership trajectory modeling algorithm
%\item Assessed the performance of this model under various simulation conditions
\item Presented at the 2017 Joint Statistical Meetings and 2016 American Society of Criminology Conference
\item Manuscript in progress
%\item Critical examination of the assumptions underlying simulation methods for trajectory models
\end{list2} 
\end{list1}




{\bf Macalester College Department of Statistics}, St. Paul, Minnesota
\begin{list1}
\item[] 
Statistics Honors Thesis, May 2014--May 2015
\begin{list2}
\vspace*{.05in}
\item
Advisor: Vittorio Addona
\item Compared classification accuracy of various combinations of dictionary learning, classification algorithms, and dimension reduction algorithms 
\item Accepted for publication
%\item Supervisor: Vittorio Addona
\end{list2} 
\end{list1}


% Commented out: MAXIMA IMA (but dates added to thesis)
% Also CKS, MN2020
\begin{comment}
{\bf Institute for Mathematics and Its Applications}, Minneapolis, Minnesota
\begin{list1}
\item[] 
Research Assistant, May 2014--July 2014
\begin{list2}
\vspace*{.05in}
\item
 Developed a model to automatically predict mode of transportation using smartphone sensor data
 \item Manipulated, cleaned, and visualized large time-series data sets in R
\item Contributed random forest methods of final model to Android smartphone application
 \item Presented research findings biweekly, created research poster and paper
%\item Supervisors: Julian Wolfson and Vittorio Addona
\end{list2} 
\end{list1}


{\bf Center for Khmer Studies}, Siem Reap, Cambodia
\begin{list1}
\item[] 
Undergraduate Research Fellow, June 2013--August 2013
\begin{list2}
\vspace*{.05in}
\item Conducted a statistical analysis of price discrimination in the bargain economy of Cambodian markets
\item Took coursework in applied social science research methodology
\item Designed an experiment to test the effects of gender and ethnicity on offered prices
\item Presented results at the Center for Khmer Studies research symposium
%\item Supervisor: Alberto P\'erez-Pereiro
\end{list2} 
\end{list1}

{\bf MN2020}, St. Paul, Minnesota
\begin{list1}
\item[] 
Education Research Fellow, January 2013--February 2013
\begin{list2}
\vspace*{.05in}
\item Analyzed local, state, and national education policy through the lens of racial and socioeconomic equity
\item Composed reports evaluating current policy and advocating for policy change
\item Published policy reports to various social media outlets with over 47,000 subscribers
\item Gathered and cleaned data for project to evaluate charter school funding and outcomes
%\item Supervisor: John Van Hecke
\end{list2}
\end{list1}
\end{comment}

% professional experiences
\section{\sc Teaching \\ Experience}

{\bf University of Washington}, Seattle, Washington
\begin{list1}
\item[] Statistics Tutor, September 2016--Present
\begin{list2}
\vspace*{.05in}
\item Drop-in tutoring provided for students in all undergraduate statistics courses, as well as related courses in other departments
\end{list2}
\end{list1}

{\bf University of Washington}, Seattle, Washington
%\vspace*{-.1in}
\begin{list1}
\item[] Teaching Assistant, September 2015--May 2016
\begin{list2}
\vspace*{.05in}
\item Statistics 221: Statistical Concepts \& Methods for the Social Sciences
%\item Prepare and teach four hours of lecture each week
%\item Host weekly office hours, focused on providing personalized and constructive feedback
%\item Assess and grade quizzes and other assignments
\end{list2}
\end{list1}


{\bf Macalester College}, St. Paul, Minnesota
%\vspace*{-.1in}
\begin{list1}
\item[] Supplemental Instructor, August 2014--December 2014
\begin{list2}
\vspace*{.05in}
\item Economics 361: Intermediate Microeconomic Analysis
\item Planned and taught an optional supplementary two-hour weekly lecture on Sundays, maintained an average attendance of 60\% of total enrollment
\item Created practice problems and study exercises for students
%\item Hosted weekly office hours
\end{list2}
\end{list1}

{\bf Macalester College}, St. Paul, Minnesota
%\vspace*{-.1in}
\begin{list1}
\item[] Teaching Assistant, September 2013--May 2014 \& January 2015--May 2015
\begin{list2}
\vspace*{.05in}
\item Mathematics 254: Probability and Mathematical Statistics
\item Economics 361: Intermediate Microeconomic Analysis
\item Economics 119: Principles of Economics
%\item Produced answer keys for weekly assignments
%\item Hosted biweekly office hours
%\item Assessed and graded course assignments
\end{list2}
\end{list1}


\section{\sc Conference Proceedings}
Erosheva, E., \textbf{Martin, B. D.}, \& Matsueda, R. L. Trajectory Models Revisited. \textit{Joint Statistical Meetings}, Baltimore, MD (July 2017).

\textbf{Martin, B. D.}, Elena Erosheva, E., \& Matsueda, R. L. A Comparison of Group-Based Trajectory Modeling Techniques. \textit{The American Society of Criminology Annual Meeting}, New Orleans, LA (November 2016).

\textbf{Martin, B. D.} Machine Learning Algorithms for Predicting Mode of Transportation Using Smartphone Sensor Data. \textit{Undergraduate Statistics Project Competition (USPROC) E-Conference} (October 2015). (Invited Plenary Speaker).

\textbf{Martin, B. D.}, Phillips, A., Berlin, H., Kinney, M., Schadler, L. SmarTrAC: Activity Detection with Smartphone Sensor Data, poster presentation at \textit{Joint Meeting in Mathematics}, San Antonio, TX (January 2015). 


\section{\sc Other Talks and \\ Presentations}


\textbf{Martin, B. D.} Learning Local Dependence in Ordered Data, \emph{Statistics PhD Oral Preliminary Examination}, presentation and defense for the University of Washington, Seattle, WA (May 2017).

\textbf{Martin, B. D.} A Comparison of Machine Learning Algorithms for Mode of Transportation Classification. \emph{Statistics Honors Thesis Defense}, public presentation and defense at Macalester College, St. Paul, MN (May 2015).



\textbf{Martin, B. D.} Price Discrimination by Race and Gender in Cambodian Bargain Economies, \textit{Center for Khmer Studies Research Symposium}, Siem Reap, Cambodia (August 2013).



\section{\sc Honours and\\ Awards}

\begin{tabular}{@{}p{0.8in}p{4in}}
2017 & University of Washington Center for Statistics and the Social Sciences Grant\\
2016--2017 & NSF Graduate Research Fellow\\
2015 & Third place in national Undergraduate Statistics Research Competition\\
2015 & Konhauser Achievement Award in Mathematics \\
&\textit{(top departmental award, Department of Mathematics, Statistics, and Computer Science, Macalester College)}\\
2015 & Vasant Sukhatme Academic Excellence Award in Economics\\& \textit{(top departmental award, Department of Economics, Macalester College)}\\
2015 & Phi Beta Kappa \textit{(honors society for the liberal arts)}\\
2014 & John M. Dozier Scholarship in Economics \\ &\textit{(top departmental award offered to juniors, Department of Economics, Macalester College)}\\
2014 & Omicron Delta Epsilon \textit{(honors society for economics)}\\
2011--2015 & DeWitt Wallace Distinguished Scholarship \textit{(Macalester College)}\\
2011--2015 & Macalester College Dean's List (all semesters)\\
2011--2015 & National Merit Scholarship \\
2011--2015 & Elks National Foundation Scholarship \textit{(national scholarship)}\\
2011 & City High School Valedictorian \textit{(school-wide scholarship)}\\
2011 & National Merit Finalist\\ 
2011 & Kiwanis Club Scholarship \textit{(regional scholarship)}\\
2011 & Silver Cord Volunteer Scholarship \textit{(school-wide scholarship)}\\
2011 & City High Scholarship \textit{(school-wide scholarship)}\\
%2011 & City High Alumni Scholarship\\
%2011 & Youth Salute Male Youth Leader of the Year 
\end{tabular}





\section{\sc Skills}
{\bf Advanced:} R, LaTeX\\
{\bf Intermediate:} C++, Bash, Stata, Excel\\
{\bf Basic:} Python, MATLAB, Mathematica, HTML


\section{\sc Relevant \\ Activities}


\begin{list1}
\item[]
\begin{list2}
\vspace*{.05in}
\item UW Statistics Department Website Committee Member (2017--present)
\item UW Statistics Department PhD student peer mentor (2017--present)
\item UW Statistical Learning Applied to Biostatistics Lab member (2017--present)
\item Macalester College Students for Education Reform Board Member (2013--2015)
\item Macalester College Students for Economic Justice Organizer (2014)
\item Macalester College slacklining organization founder and president (2014--2015)
\end{list2}
\end{list1}




\begin{comment}
\section{\sc Extra-- \\ Cirriculars} 




%{\bf University of Washington}, Seattle, Washington
%\vspace*{-.1in}
%\begin{list1}
%\item[] 
%\begin{list2}
%\vspace*{.05in}
%\item Attendee of two weekly machine learning seminars
%\end{list2}
%\end{list1}


{\bf Macalester College}, St. Paul, Minnesota
%\vspace*{-.1in}
\begin{list1}
\item[]
\begin{list2}
\vspace*{.05in}
\item Board member of Macalester College Students for Education Reform
\item Organizer of Students for Economic Justice
\item Founder and president of Macalester College student slacklining organization
\end{list2}
\end{list1}
\end{comment}

% Interests section currently commented out
\begin{comment}
\section{\sc Interests}
\begin{list1}
\item[] 



\begin{list2}
\item Biking, hiking, board games, and slacklining
\end{list2} 
\end{list1}
\end{comment}

\end{resume}
\end{document}
